Vertical and oblique cultural transmission fluctuating in time and in space

### 2018-10-30 ms/ms_sunnyvale.tex
new par by MWF

>>>>

The interaction between spatially varying selection and transmission is shown in Figures \ref{fig:migration_rho} and \ref{fig:migration_m} to depend on migration in a complex way.
However, our two-deme model does not exhibit the kind of complexity seen in \citet{Ram2018}, where the period of environmental fluctuation determined whether the vertical transmission rate $\rho$ that maximized the population mean fitness was the same as the evolutionarily stable value.
We can speculate that a model with more sub-populations and a more geographically complicated fitness regime might show less predictable relationships between transmission and selection.
